 \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Tribe: A networking site (Earlier dubbed as FamJam):  \href{https://github.com/thesidshah/famjam}{[code]}} $|$ \emph{HTML, CSS, JS (Node, React)}}{Jun. 2022}
          \resumeItemListStart
            \resumeItem{Engineered a website for groups of friends, enabling users to post memories.}
            \resumeItem{Leveraged frameworks such as NodeJS for back-end, React JS for front-end, and customized CSS using bootstrap themes. Utilized BrowserRouter, Redux consistent state }
            % \resumeItem{Added capabilities to track todos and expenses for the group, for example, Bring the BBQ for Sunday's meet-up.}
            \resumeItem{Streamlined sign-in process with google-OAuth2.0 and used Google APIs to generate calendar events.}
          \resumeItemListEnd
          \resumeProjectHeading{\textbf{Twitter clone}}{May 2022}
      \resumeItemListStart
        \resumeItem{Experimented with JavaScript, React JS, Node JS and CSS frameworks such as Bootstrap.}
        \resumeItem{Included a timeline-like page, a trending page, and a search bar along with a profile page.}
        \resumeItem{Used GitHub: versioning, Netlify: continuous integration \& deployment and Heroku: hosting the back-end.}
      \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Dungeons and Demons} $|$ \emph{Java, Java Swing}}{Dec. 2021}
          \resumeItemListStart
            \resumeItem{Developed a game that creates 1000+ randomized variants of maps of the dungeon.}
            \resumeItem{Applied Model View Controller and Factory design pattern to make the code adaptive as well extensible.}
            \resumeItem{Featured 3 levels of game adversaries: Pit, Wumpus, Moving Wumpus and 10+ types of rewards.}
          \resumeItemListEnd
              \resumeProjectHeading
          {\textbf{\href{www.suyoglifecare.org}{\underline{Suyog Life Care's website}}} $|$ \emph{HTML, CSS, Bootstrap, JS}}{May 2021}
          \resumeItemListStart
            \resumeItem{Designed, developed and tested an interactive adaptive website that increased viewership by 100\%.}
            \resumeItem{Integrated SendGrid and Wix for efficiently delivering reports to patients within 120 seconds of generation on an average as well as curated dashboards for promotional campaigns.}
            \resumeItem{Presented a dynamically priced shopping experience option to select from the 500+  diagnostic tests.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd