%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Software Engineer Intern}{Oct. 2022 - Dec. 2022}
    {SS\&C IntraLinks}{Waltham, MA}
    \resumeItemListStart
    \resumeItem{Built interactive internal documentation for components in React by porting 30+ elements to an open-source framework and adapting industry-wide standards like Component Story Formats (CSF).} 
    \resumeItem{Adapted current and recent frameworks with Model-View-Controller architecture such as React, Backbone JS, and composed CSS libraries using preprocessed scripting language Sass.}
    \resumeItem{Optimized  VDRPro's front-end following the CI/CD methodology using tools such as Jenkins for Deployment, Bitbucket for versioning, JIRA for Kanban boards and story tracking.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Software Associate Engineer}{Dec. 2020 -- Aug. 2021}
      {Globant Pvt Ltd}{Pune, IN}
      \resumeItemListStart
        % \resumeItem{Developed solutions in JavaScript for high-profile projects involving the leadership of fortune 500 companies.}
        % \resumeItem{Recognized and recommended by the team along with a letter of recommendation from the manager.}
        % \resumeItem{Effective multitasking and prioritization by working on multiple projects simultaneously.}
        \resumeItem{Created an instance of ServiceNow to make a unified platform for the company to streamline work and gather insights from operations across the world, named 'The Global Enhancement Project'.}
        \resumeItem{ The initiative \emph{saved an approximate 250+ man-hours} of effort and enabled the leadership to have a detailed view of live progress and integrated with PowerBI the project enhanced user experience, increasing viewership by at least 20\%.}
        \resumeItem{Employed practices such as Rapid Deployment, and Scrum-based Agile methodology to create 50+ ServiceNow based dashboards, customized forms.}
    \resumeItemListEnd
      \resumeSubheading
      {Research Intern}{Sep. 2019 -- Feb. 2020}
      {Visava Labs (Delta Interiors Pvt Ltd)}{Pune, IN}
      \resumeItemListStart
      
        % \resumeItem{Explored methods to generate floor plans based on \emph{colorized apartment plans.}}
        \resumeItem{Developed an expert-based system in Java that generates 100+ possible configurations for each input permutation.}
        \resumeItem{Lead the team's research in \textbf{Generative Adversarial Networks} (\emph{GANs}) and its application to \emph{3D floor plan generation} at the intersection of Architecture and Technology as well as adapted it to practical implementation.}
        % \resumeItem{Created an \textbf{Android application} that localizes the user and generates specific outputs. \textbf{Secured} first round of \textbf{funding} for the startup. }
         \resumeItem{Designed an \textbf{Android application} that accepts various input constraints such as budget, area, etc, and displays a detailed list of material required based on the location, 2D, and 3D floor plans.}
         \resumeItem{ \textbf{Secured} first round of (80\%) \textbf{funding} for the startup.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
    
    \section{Academic Experience}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Graduate Teaching Assistant}{Sep. 2021 -- May 2022}
      {Northeastern University}{Boston, MA}
      \resumeItemListStart
      \resumeItem{Collaborated with the instructor and 3 other TAs to review coursework, develop the course further, and grade assignments for \emph{Foundation's of Artificial Intelligence.}}
        \resumeItem{Advised a class of 200+ students as they studied the depths of \emph{Computer Systems}, particularly topics such as different parts of an Operating System, C data structures, and seven layers of a file system.}
    \resumeItemListEnd
     
    \resumeSubheading
      {Undergraduate Research Assistant}{Jun. 2018 -- May 2020}
      {Pune University}{Pune, IN}
      \resumeItemListStart
        \resumeItem{Implemented 3 machine learning pipelines for Anomaly Detection in Software Defined Networking(\emph{SDN}) and gave a seminar on the basic blocks of a SDN 
        %as well as how to incorporate the technology in 5G networks
        to a class of 100+ attendees.}
        \resumeItem{Peer-reviewed and published the work in IEEE. (\href{https://ieeexplore.ieee.org/document/9128786/}{\color{blue}{\underline{link}}})}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd